Think deep for reef resilience

### 2025-08-14 paper/paper_draft.qmd
Add RRAP citation and manually update years in .bib where missing
Sometimes citations carried over from Zotero are missing years and will render in word as n.d.

In addition to the usual challenges of deriving data from satellite imagery, it is
acknowledged that there is high potential for misalignment between the bathymetry data and
GBRMPA reef outlines. Hammerton and Lawrey [-@hammerton], for example, identified 120 false
positives, where features identified as reefs were in actuality sand banks or rocky reefs
(rather than coral reefs). Reefs with bathymetry data of less than 5% of its indicative area
were excluded from analysis to ensure analyses were not conducted on reefs with no data
coverage (see @sfig-depth-cutoff). The existing GBRMPA reef outlines were adopted to align
with other ongoing modelling and analyses conducted as part of the Reef Restoration and
Adaptation Program \[RRAP; <https://gbrrestoration.org>\] **\[TODO: PROPER CITATION OF
RRAP\]**.

>>>>

In addition to the usual challenges of deriving data from satellite imagery, it is
acknowledged that there is high potential for misalignment between the bathymetry data and
GBRMPA reef outlines. Hammerton and Lawrey [-@hammerton2025], for example, identified 120
false positives, where features identified as reefs were in actuality sand banks or rocky
reefs (rather than coral reefs). Reefs with bathymetry data of less than 5% of its
indicative area were excluded from analysis to ensure analyses were not conducted on reefs
with no data coverage (see @sfig-depth-cutoff). The existing GBRMPA reef outlines were
adopted to align with other ongoing modelling and analyses conducted as part of the Reef
Restoration and Adaptation Program (<https://gbrrestoration.org>; [@thereef]).
